251 MA

### 2023-03-06 code/process.Rmd
working on code

```{r}
d <- readxl::read_xlsx(here("data","raw_data.xlsx"), 
                       sheet="aligned data", skip=1) |> 
  select(target_lastauthor_year, sensitivity, include,
         status, academic_year, subfield, target_year, stanford_internal, 
         open_data, open_materials, target_on_turk, replication_on_turk, 
         within_between, single_vignette, repeated_measure,
         target_N, target_test, target_raw_stat, target_pvalue, target_ES_type, 
         target_ES_value, same_dir, replication_N, # replication_test
         replication_raw_stat, replication_pvalue, replication_ES_type, 
         replication_ES_value, replicated_instructor_code, replicated_report_code,
         adjudicated_replication_code)

@@

test |> filter(is.na(target_ES)) |> filter(!is.na(target_raw_stat)) |>  pull(target_raw_stat)

test |> filter(is.na(rep_ES)) |> filter(!is.na(replication_raw_stat)) |> pull(replication_raw_stat)
```

@@

```{r}
d_es_predInt <- d_es |> 
  rowwise() |> 
  mutate(predInt = do_pred_int(target_ES, target_SE, rep_ES, rep_SE),
         p_orig = do_p_orig(target_ES, target_SE, rep_ES, rep_SE),
         sub_rep = do_subjective_rep(replicated_instructor_code, 
                                     replicated_report_code, 
                                     adjudicated_replication_code))
```

@@

```{r}
d_es_predInt |> 
  filter(target_d_calc < 5, rep_d_calc < 5) |>
  ggplot(aes(x=target_d_calc, y=rep_d_calc, color=sub_rep))+
  geom_point() +
  geom_abline(slope=1, intercept=0, lty = 2)+
  geom_smooth(method = "lm") + 
  geom_hline(yintercept = 0, lty = 2)+
  scale_color_viridis(discrete=F, direction = -1, 
                      name = "Subjective Replication Success")+
  labs(color="subrep", x="Original SMD", y="Replication SMD") + 
  theme(legend.position = "bottom")
```

@@

# Models

@@

```{r, eval=F}
tier1_subjective <- brm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                          (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                             z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
                        family="cumulative", # runs on 1-5 data
                        data=data_tier1,
                        file=here(model_location, "tier1_subjective"),
                        prior=priors, 
                        control=list(adapt_delta=.99),
                        backend="cmdstanr"
)
```

## Exploring stuff for Tier 1

```{r}
tier1_subjective_beta<- brm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                              z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                              (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                                 z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
                            family="beta", # runs on 1-5 data
                            data=data_tier1 |> mutate(sub_rep=(sub_rep-1)/4*.98+.01),
                            file=here(model_location, "tier1_subjective_beta"),
                            prior=strong_priors, 
                            control=list(adapt_delta=.99),
                            backend="cmdstanr"
)

### frequentism

regularized
```{r}
predictors <- data_tier1 |> select(z_pub_year, open_data, open_mat, stanford, change_platform, 
                                   z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials)

yvals <- data_tier1 |> mutate(sub_rep=(sub_rep-1)/4) |> pull(sub_rep)
lasso_linear <- cv.glmnet(predictors, yvals |> as.matrix(), 
                          family="gaussian", alpha=1)

```{r}
library("lattice")
dat <- data_tier1 |> mutate(is.cog=ifelse(subfield=="cognitive", 1,0),
                            is.soc=ifelse(subfield=="social", 1,0),
                            is.other=ifelse(subfield=="other-psych", 1,0),
                            is.non=ifelse(subfield=="non-psych",1,0)) |> 
  select(is.cog, is.soc, is.other, is.non, z_pub_year, open_data, open_mat, stanford, change_platform, 
         z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials)

# reduce the size of correlation matrix
melted_corr_mat <- melt(corr_mat)
# head(melted_corr_mat)

# plotting the correlation heatmap
library(ggplot2)
ggplot(data = melted_corr_mat, aes(x=Var1, y=Var2,
                                   fill=value)) + scale_fill_viridis()+
  geom_tile(alpha=.7)+theme(axis.text.x = element_text(angle = 40, vjust = 1, hjust=1))+geom_text(aes(label=value), size=3)

corr_mat |> as_tibble(rownames="value2") |> pivot_longer(cols=!value2, names_to="value1", values_to = "corr") |> arrange(corr) |> filter(value2 <value1) |> View()

corr_mat |> as_tibble(rownames="value2") |> pivot_longer(cols=!value2, names_to="value1", values_to = "corr") |> arrange(desc(corr)) |> filter(value2 <value1)

## Tier 2 and 3
```{r, eval=F}
tier2_predint <- brm(pred_int ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                       z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                       (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
                     family="bernoulli",
                     data=data_tier2,
                     file=here(model_location, "tier2_predint"),
                     prior=priors, 
                     control=list(adapt_delta=.99),
                     backend="cmdstanr")
```

@@

@@

```{r}
normal_priors <- c(set_prior("horseshoe(3)", class="b"),
                   set_prior("normal(0,.5)", class="sd"))

@@

>>>>

```{r}
d <- readxl::read_xlsx(here("data","raw_data.xlsx"), 
                       sheet="aligned data", skip=1) |> 
  select(target_lastauthor_year, sensitivity, include,
         status, academic_year, subfield, target_year, stanford_internal, 
         open_data, open_materials, target_on_turk, replication_on_turk, 
         within_between, single_vignette, repeated_measure,
         target_N, target_raw_stat, same_dir, replication_N,
         replication_raw_stat, replicated_instructor_code, replicated_report_code,
         adjudicated_replication_code)

@@

test |> filter(is.na(target_ES)) |> filter(!is.na(target_raw_stat)) |> select(target_lastauthor_year, target_raw_stat)

test |> filter(is.na(rep_ES)) |> filter(!is.na(replication_raw_stat)) |> select(target_lastauthor_year, replication_raw_stat)

@@

d_es <-  test |> 
  mutate(target_d_calc=abs(target_d_calc),
         target_ES=abs(target_ES),
         rep_d_calc=case_when(
           same_dir=="yes" ~ abs(rep_d_calc),
           same_dir=="no" ~-abs(rep_d_calc),
           T ~ as.numeric(NA)
         ),
         rep_ES=case_when(
           same_dir=="yes" ~ abs(rep_ES),
           same_dir=="no" ~-abs(rep_ES),
           T ~ as.numeric(NA)
         ))

d_es_predInt <- d_es |> 
  rowwise() |> 
  mutate(predInt = do_pred_int(target_ES, target_SE, rep_ES, rep_SE),
         p_orig = do_p_orig(target_ES, target_SE, rep_ES, rep_SE),
         sub_rep = do_subjective_rep(replicated_instructor_code, 
                                     replicated_report_code, 
                                     adjudicated_replication_code))
```

@@

```{r}
d_es_predInt |> 
  filter(target_d_calc < 5, rep_d_calc < 5) |>
  ggplot(aes(x=target_d_calc, y=rep_d_calc, color=sub_rep))+
  geom_point() +
  geom_abline(slope=1, intercept=0, lty = 2)+
  geom_smooth(method = "lm") + 
  geom_hline(yintercept = 0, lty = 2)+
  scale_color_viridis(discrete=F, direction = -1, 
                      name = "Subjective Replication Success")+
  labs(color="subrep", x="Original SMD", y="Replication SMD") + 
  theme(legend.position = "bottom")

@@

# Pre-reg'd Models

@@

```{r, eval=T}
tier1_subjective <- brm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                          (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                             z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
                        family="cumulative", # runs on 1-5 data
                        data=data_tier1,
                        file=here(model_location, "tier1_subjective"),
                        prior=priors, 
                        control=list(adapt_delta=.99),
                        backend="cmdstanr"
)
```

```{r}
library(tidybayes)
tier1_subjective |> 
gather_draws(`b_[a-zA-Z_(): ]+`, regex=TRUE) |> mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |> 
  ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate)) + geom_vline(xintercept=0)+
  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI")+theme(axis.text=element_text(size=11))
```

```{r, eval=F}
tier2_predint <- brm(pred_int ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                       z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                       (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
                     family="bernoulli",
                     data=data_tier2,
                     file=here(model_location, "tier2_predint"),
                     prior=priors, 
                     control=list(adapt_delta=.99),
                     backend="cmdstanr")
```

@@

```{r}
library("lattice")
dat <- data_tier1 |> mutate(is.cog=ifelse(subfield=="cognitive", 1,0),
                            is.soc=ifelse(subfield=="social", 1,0),
                            is.other=ifelse(subfield=="other-psych", 1,0),
                            is.non=ifelse(subfield=="non-psych",1,0)) |> 
  select(is.cog, is.soc, is.other, is.non,stanford, z_pub_year, open_data, open_mat,  change_platform, 
         z_log_ratio_ss, z_log_sample, single_vignette, z_log_trials, is_within, )

# reduce the size of correlation matrix
melted_corr_mat <-melt(corr_mat)
# head(melted_corr_mat)

# plotting the correlation heatmap
library(ggplot2)
ggplot(data = melted_corr_mat, aes(x=Var1, y=Var2,
                                   fill=value)) + #scale_fill_viridis()+
  scale_fill_gradient2(low="#440154",high="#FDE725FF")+
  geom_tile(alpha=.7)+theme(axis.text.x = element_text(angle = 40, vjust = 1, hjust=1))+geom_text(aes(label=value), size=3)+
  labs(x="", y="", fill="Correlation")

#corr_mat |> as_tibble(rownames="value2") |> pivot_longer(cols=!value2, names_to="value1", values_to = "corr") |> arrange(corr) |> filter(value2 <value1) |> View()

#corr_mat |> as_tibble(rownames="value2") |> pivot_longer(cols=!value2, names_to="value1", values_to = "corr") |> arrange(desc(corr)) |> filter(value2 <value1)

## other bayesian models

```{r, eval=F}
tier1_subjective_beta<- brm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                              z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                              (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                                 z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
                            family="beta", # runs on 1-5 data
                            data=data_tier1 |> mutate(sub_rep=(sub_rep-1)/4*.98+.01),
                            file=here(model_location, "tier1_subjective_beta"),
                            prior=strong_priors, 
                            control=list(adapt_delta=.99),
                            backend="cmdstanr"
)

## frequentism

regularized
```{r}
predictors <- data_tier1 |> mutate(social=ifelse(subfield=="social", 1,0),other=ifelse(subfield=="other-psych",1,0), non=ifelse(subfield=="non-psych", 1,0)) |> 
  select(z_pub_year, open_data, open_mat, stanford, change_platform, social, other, non, 
                                   z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials) |> as.matrix()

yvals <- data_tier1 |> mutate(sub_rep=(sub_rep-1)/4) |> pull(sub_rep)
#lasso_linear <- cv.glmnet(predictors, yvals |> as.matrix(),       family="gaussian", alpha=1)

```{r}
library(ggrepel)
library(ggthemes)
to_plot <- lasso_linear2$beta |> as.matrix() |> as.tibble(rownames="var") |> pivot_longer(`s0`:`s71`) |> mutate(time=str_sub(name, 2,-1) |> as.numeric())

ggplot(to_plot, aes(x=time, y=value, color=var, label=var))+geom_line()+geom_label_repel(data=to_plot |> filter(time==70), min.segment.length = 100, nudge_x = 10, na.rm = TRUE)+ theme(legend.position="none")+ scale_color_tableau("Classic 20")+
  coord_cartesian(xlim=c(0,80), ylim=c(-.2, .3))+theme(axis.text.x=element_blank(), axis.title.x=element_blank(), axis.ticks.x=element_blank())

regularized p_orig

```{r}
dat <- data_tier2 |> filter(!is.na(p_orig)) |>  mutate(social=ifelse(subfield=="social", 1,0),other=ifelse(subfield=="other-psych",1,0), non=ifelse(subfield=="non-psych", 1,0))
predictors <- dat |> select(z_pub_year, open_data, open_mat, #stanford, 
                            change_platform, social, non, other,
                                   z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials) |> as.matrix()

yvals <- dat|> pull(p_orig)

lasso_linear_porig <- glmnet(predictors, yvals, 
                        family="gaussian", alpha=1)

yvals <- dat |> pull(predInt)

lasso_linear_predint <- glmnet(predictors, yvals, 
                        family="binomial", alpha=1)
```

```{r}
to_plot <- lasso_linear_porig$beta |> as.matrix() |> as.tibble(rownames="var") |> pivot_longer(`s0`:`s72`) |> mutate(time=str_sub(name, 2,-1) |> as.numeric())

ggplot(to_plot, aes(x=time, y=value, color=var, label=var))+geom_line()+geom_label_repel(data=to_plot |> filter(time==70), min.segment.length = 100, nudge_x = 10, na.rm = TRUE)+ theme(legend.position="none")+ scale_color_tableau("Classic 20")+
  coord_cartesian(xlim=c(0,80), ylim=c(-.2, .3))+theme(axis.text.x=element_blank(), axis.title.x=element_blank(), axis.ticks.x=element_blank())
```

```{r}
to_plot <- lasso_linear_predint$beta |> as.matrix() |> as.tibble(rownames="var") |> pivot_longer(`s0`:`s58`) |> mutate(time=str_sub(name, 2,-1) |> as.numeric())

ggplot(to_plot, aes(x=time, y=value, color=var, label=var))+geom_line()+geom_label_repel(data=to_plot |> filter(time==55), min.segment.length = 100, nudge_x = 10, na.rm = TRUE)+ theme(legend.position="none")+ scale_color_tableau("Classic 20")+
  coord_cartesian(xlim=c(0,70))+theme(axis.text.x=element_blank(), axis.title.x=element_blank(), axis.ticks.x=element_blank())

@@

```{r, eval=F}
normal_priors <- c(set_prior("horseshoe(3)", class="b"),
                   set_prior("normal(0,.5)", class="sd"))

@@

## Individual predictor - outcome correlations

### Sub_rep
```{r}
dat <- data_tier1 |> mutate(sub_rep=((sub_rep-1)/4) |> factor(levels=c("0","0.25", "0.5", "0.75", "1")))

ggplot(dat, aes(x=sub_rep, fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme(legend.position = "none")+labs(y="Count", x="Subjective Replication score")

ggplot(dat, aes(x=subfield, fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)

dat |> mutate(open_mat=ifelse(open_mat, "Open materials", "No open materials"), open_data=ifelse(open_data, "Open data", "No open data")) |> ggplot( aes(x=open_data |> factor(), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+facet_wrap(.~open_mat)+theme(axis.title.x=element_blank())

 ggplot(dat, aes(x=factor(stanford), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)

ggplot(dat, aes(x=factor(change_platform), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)

ggplot(dat, aes(x=ifelse(is_within, "Within", "Between"), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme(axis.title.x=element_blank())

ggplot(dat, aes(x=ifelse(single_vignette, "1 vignette", "multiple vignettes"), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme(axis.title.x=element_blank())
```

```{r}
# using d for model to get non-z-scored version
ggplot(d_for_model, aes(x=pub_year, y=sub_rep, color=sub_rep))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()

ggplot(d_for_model, aes(x=log_ratio_ss, y=log_sample, color=sub_rep))+geom_point()+scale_color_viridis()

ggplot(d_for_model, aes(x=log_ratio_ss, y=sub_rep, color=sub_rep))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()

ggplot(d_for_model, aes(x=log_sample, y=sub_rep, color=sub_rep))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()

ggplot(d_for_model, aes(x=log_trials, y=sub_rep, color=sub_rep))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()

### Pred_int
Note: predInt may not be reliably calculated in some cases. Dealing with numbers is hard!

```{r}
dat <- d_for_model |> filter(!is.na(predInt)) |>  mutate(predInt=predInt |> factor())

ggplot(dat, aes(x=predInt, fill=predInt))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)

ggplot(dat, aes(x=subfield, fill=predInt))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)

ggplot(dat, aes(x=open_data |> factor(), fill=predInt))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+facet_wrap(.~str_c("open_mat ",open_mat))

ggplot(dat, aes(x=factor(stanford), fill=predInt))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)

ggplot(dat, aes(x=factor(change_platform), fill=predInt))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)

ggplot(dat, aes(x=factor(is_within), fill=predInt))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)

ggplot(dat, aes(x=factor(single_vignette), fill=predInt))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
```

```{r}
# using d for model to get non-z-scored version
dat <- d_for_model |> filter(!is.na(predInt))

ggplot(dat, aes(x=pub_year, y=predInt, color=predInt))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()

ggplot(dat, aes(x=log_ratio_ss, y=log_sample, color=predInt))+geom_point()+scale_color_viridis()

ggplot(dat, aes(x=log_ratio_ss, y=predInt, color=predInt))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()

ggplot(dat, aes(x=log_sample, y=predInt, color=predInt))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()

ggplot(dat, aes(x=log_trials, y=predInt, color=predInt))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()

### P_orig
Note: predInt may not be reliably calculated in some cases. Dealing with numbers is hard!

```{r}
dat <- d_for_model |> filter(!is.na(p_orig)) |> mutate(p_orig_bin=ifelse(p_orig>.05, ">.05", "<.05"))

ggplot(dat, aes(x=p_orig, fill=p_orig_bin))+geom_histogram()+scale_fill_viridis(discrete=T)

ggplot(dat, aes(x=subfield, fill=p_orig_bin))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)

ggplot(dat, aes(x=open_data |> factor(), fill=p_orig_bin))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+facet_wrap(.~str_c("open_mat ",open_mat))

ggplot(dat, aes(x=factor(stanford), fill=p_orig_bin))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)

ggplot(dat, aes(x=factor(change_platform), fill=p_orig_bin))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)

ggplot(dat, aes(x=factor(is_within), fill=p_orig_bin))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)

ggplot(dat, aes(x=factor(single_vignette), fill=p_orig_bin))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)
```

```{r}
# using d for model to get non-z-scored version
dat <- d_for_model |> filter(!is.na(p_orig))

ggplot(dat, aes(x=pub_year, y=p_orig, color=p_orig))+geom_point()+geom_smooth(method="lm")+scale_color_viridis()

ggplot(dat, aes(x=log_ratio_ss, y=log_sample, color=p_orig))+geom_point()+scale_color_viridis()

ggplot(dat, aes(x=log_ratio_ss, y=p_orig, color=p_orig))+geom_point()+geom_smooth(method="lm")+scale_color_viridis()

ggplot(dat, aes(x=log_sample, y=p_orig, color=p_orig))+geom_point()+geom_smooth(method="lm")+scale_color_viridis()

ggplot(dat, aes(x=log_trials, y=p_orig, color=p_orig))+geom_point()+geom_smooth(method="lm")+scale_color_viridis()

### TODO predictive

```{r}
# cognitive, within, foobar trials, foobar participants, etc etc

back_convert

fake_data <- tribble(
   ~subfield, ~open_data, ~open_mat, ~change_platform, ~is_within, ~single_vignette, ~log_sample, ~log_trials,
  "cognitive", 1,         1,         0,                1,          0,                log(50),    log(100),
  "cognitive", 0,         0,         0,                1,          0,                log(50),    log(100),
  "cognitive", 1,         1,         0,                1,          0,                log(50),    log(100),
   "social", 0,         0,         1,                0,          1,                log(30),     log(1),
) |> mutate(academic_year="2022-2023", pub_year=2022, stanford=0, log_ratio_ss=0,
            z_log_sample=(log_sample-back_convert$mean_log_sample)/back_convert$sd_log_sample,
            z_log_trials=(log_trials-back_convert$mean_log_trials)/back_convert$sd_log_trials,
            z_pub_year=(pub_year-back_convert$mean_pub_year)/back_convert$sd_pub_year,
            z_log_ratio_ss=(log_ratio_ss-back_convert$mean_log_ratio_ss)/back_convert$sd_log_ratio_ss, sub_rep=NA) |> 
select(academic_year, sub_rep, 
         z_pub_year, subfield, open_data, open_mat, stanford, change_platform, z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials)

foo <- predict(tier1_subjective, newdata=fake_data)

bar <- fitted(tier1_subjective,newdata=fake_data)
```
